Technical Report

### 2018-05-30 fully-abstract-comp/technical-report.tex
Finish proof by adding an extra technical requirement to codereg.

\begin{equation*}
  H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_) \; \hat{W} = \left\{\npair{(\code,\code)} \middle|
    \begin{array}{l}
    \dom(\code) = [\aaddr,\baddr] \wedge \\
    \dom(\code) \subseteq \ta \vee (\dom(\code)\mathrel{\#} \ta \wedge \sigrets = \emptyset) \wedge \\
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code 
    \end{array}
  \right\}
\end{equation*}

@@

\begin{lemma}[Code region for untrusted components stronger than standard safe memory region]
  \label{lem:codereg-untrusted-stdreg}
  If
  \begin{itemize}
  \item $\emptyset\neq\dom(\mscode) \mathrel{\#} \ta$
  \end{itemize}
  then $\codereg{\sigrets,\sigcloss,\mscode,\gc} \nsubeq \stdreg{\dom(\mscode),\gc}{\pur}$ 
\end{lemma}
\begin{proof}
  Take $\hat{W}$, then we need to prove that
  \begin{equation*}
    H^\mathrm{code}\ ;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W} \nsubeq H_{\dom(\mscode)}^{\mathrm{std},\square}\;\hat{W}
  \end{equation*}
  So take $\npair{\ms_S,\ms_T} \in H^\mathrm{code}\ ;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W}$, then we know that
  \begin{itemize}
  \item $\ms_S = \ms_T = \mscode$ 
  \item $\dom(\mscode) =[\aaddr,\baddr]$
  \item $\dom(\mscode) \subseteq \ta \vee (\dom(\mscode)\mathrel{\#} \ta \wedge \sigrets = \emptyset)$, but we know that $\emptyset \neq\dom(\mscode) \mathrel{\#} \ta$, so we get that $\sigrets = \emptyset$.
  \item $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode$
  \end{itemize}

@@

  We take $S$ to map every address to $\purePart{\hat{W}}$, except for a single one that we map to $\hat{W}$.
  Take $\aaddr\in\dom(\mscode)$, $n'<n$.
  By Lemmas~\ref{lem:purePart-duplicable}, \ref{lem:oplus-future} and \ref{lem:monotonicity}, it now suffices to prove that $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(\purePart{\hat{W}})$.

  From $\sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode$ and the fact that $\sigrets = \emptyset$, we know that for any $\aaddr\in\dom(\mscode)$, we have that $\emptyset,\emptyset,\sigcloss \vdash_{\mathrm{comp-code}} \mscode,\aaddr$.
  By definition, this last judgement implies that one of the following cases holds:
  \begin{itemize}
  \item $\mscode(a) \in\ints$ and an omitted extra fact.  It follows trivially that $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(\purePart{\hat{W}})$.
  \item 
    $\mscode(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}$ and $[\sigma_\baddr,\sigma_\eaddr] \subseteq \sigcloss$.

    By definition of $\lrv$, it suffices to show that $\exists r \in
    \dom(\pwheap)$ such that $\pwheap(r) = (\pure,\_,H_\sigma)$ and $H_\sigma \;
    \sigma' \nequal \lrv$.

    \dominique{TODO: we need to know that our code region is in $\hat{W}$?}

    Then we can use Lemma~\ref{lem:untrusted-codereg-sealed-vals-safe}.
  \end{itemize}
\end{proof}

>>>>

\begin{equation*}
  H^\mathrm{code} \; \sigrets \; \sigcloss \; \code \; (\ta,\_) \; \hat{W} = \left\{\npair{(\code,\code)} \middle|
    \begin{array}{l}
    \dom(\code) = [\aaddr,\baddr] \wedge \\
    \dom(\code) \subseteq \ta \vee (\dom(\code)\mathrel{\#} \ta \wedge \sigrets = \emptyset) \wedge \\
      \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \code \wedge\\
      \forall a \in \dom(\code), n' < n \ldotp\npair[n']{(\code(a),\code(a))} \in \lrv(\purePart{\xi(\hat{W})})
    \end{array}
  \right\}
\end{equation*}

@@

\begin{lemma}[Code region for untrusted components stronger than standard safe memory region]
  \label{lem:codereg-untrusted-stdreg}
  If
  \begin{itemize}
  \item $\emptyset\neq\dom(\mscode) \mathrel{\#} \ta$
  \end{itemize}
  then $\codereg{\sigrets,\sigcloss,\mscode,\gc} \nsubeq \stdreg{\dom(\mscode),\gc}{\pur}$ 
\end{lemma}
\begin{proof}
  Take $\hat{W}$, then we need to prove that
  \begin{equation*}
    H^\mathrm{code}\ ;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W} \nsubeq H_{\dom(\mscode)}^{\mathrm{std},\square}\;\hat{W}
  \end{equation*}
  So take $\npair{\ms_S,\ms_T} \in H^\mathrm{code}\ ;\sigrets\;\sigcloss\;\mscode\;\gc \; \hat{W}$, then we know that
  \begin{itemize}
  \item $\ms_S = \ms_T = \mscode$ 
  \item $\dom(\mscode) =[\aaddr,\baddr]$
  \item $\dom(\mscode) \subseteq \ta \vee (\dom(\mscode)\mathrel{\#} \ta \wedge \sigrets = \emptyset)$, but we know that $\emptyset \neq\dom(\mscode) \mathrel{\#} \ta$, so we get that $\sigrets = \emptyset$.
  \item For all $a \in \dom(\code)$, $n'<n$, $\npair[n']{(\code(a),\code(a))} \in \lrv(\purePart{\xi(\hat{W})})$
  \end{itemize}

@@

  We take $S$ to map every address to $\purePart{\hat{W}}$, except for a single one that we map to $\hat{W}$.
  The result then follows by Lemmas~\ref{lem:purePart-duplicable}, \ref{lem:oplus-future} and \ref{lem:monotonicity} and the above fact that for all $a \in \dom(\code)$, $n'<n$, $\npair[n']{(\code(a),\code(a))} \in \lrv(\purePart{\xi(\hat{W})})$.
\end{proof}
